Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-06-19 automatica/paper.tex
nomenclature

The first effect of this new equation is that the matrix is no longer upper diagonal. We must therefore compensate for the errors introduced in order to find a stable solution.
We can use Gershgoring disks to limit the error in the expected eigenvalues. Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$ (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound for any eigenvalue in $\mat{A}_e$.
Then $\forall i \in [1\ n], |\lambda_{oi}-\hat{\lambda}_{oi}|<\delta_o$,where $\lambda_{oi}$ are the true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of the perturbed observer. We note that in the case of stability we only care about the error with respect to the unit circle, which is equivalent to upper bounding the estimation of the largest eigenvalue. Hence given a desired upper value $\overline{\lambda}$, we apply Iurys criterion on the polynomial.
\begin{equation}
P_o'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
\end{equation}
Inthe case of the reachable eigenvalues, the procedure is the same except that we obtain our bound $\delta_c=\max(|\mat{A}_{e*i}+\mat{B}_{e*i}|_2)$ (\emph{i.e.} the largest column norm in $[\mat{A}_e\ \mat{B}_e]^T$) and apply Jury's Criterion over 
\begin{equation}
P_r'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
\end{equation}

>>>>

The first effect of this new equation is that the matrix is no longer upper diagonal. We must therefore compensate for the errors introduced in order to find a stable solution.
We can use Gershgoring disks to limit the error in the expected eigenvalues. Let $\delta_o=\max(|\mat{A}_{ei*}|_2)$ (\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound for any eigenvalue in $\mat{A}_t$ that corresponds to the observer.
Then $\forall i \in [1\ n], |\lambda_{oi}-\hat{\lambda}_{oi}|<\delta_o$,where $\lambda_{oi}$ are the true eigenvalues of the observer and $\hat{\lambda}_{oi}$ the eigenvalues of the perturbed observer. We note that in the case of stability we only care about the error with respect to the unit circle, which is equivalent to upper bounding the estimation of the largest eigenvalue. Hence given a desired upper value $\overline{\lambda}$, we apply Iurys criterion on the polynomial.
\begin{equation}
P_o'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
\end{equation}
Inthe case of the reachable eigenvalues, the procedure is the same except that we obtain our bound $\delta_c=\max(|\mat{A}_{e*i}+\mat{B}_{e*i}|_2)$ (\emph{i.e.} the largest column norm in $[\mat{A}_e\ \mat{B}_e]^T$) and apply Jury's Criterion over 
\begin{equation}
P_r'=\sum_{j=0}^n c_j\overline{\lambda'}^{n-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
\end{equation}
